---
title: "Census API Work"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Access Census Data Files
library(tidycensus)

# Access Tiger Files (census map files)
library(tigris)

# work with spatial objects, note: sf = "simple features"
library(sf)
library(sp)

# other useful packages
library(tidyverse)
library(viridis)
library(dplyr)
library(stringr)
#census_api_key("eb2fc06ce454a7690661a2186c95aaa320215498", install = TRUE)
# First time, reload your environment so you can use the key without restarting R.
readRenviron("~/.Renviron")
# Go Get my Census API Key from my environmental variables
Sys.getenv("CENSUS_API_KEY")
```

```{r}
demographic_vars <- c(
Population = "B02001_001",
Hispanic = "B03002_013",
White = "B02001_002",
Black = "B02009_001",
Asian = "B02015_001",
Median_Inc = "B06011_001"
)
# access the census data
AlleghenyBlockGroups <- get_acs(geography = "cbg", 
              variables = demographic_vars, 
              state = "PA", 
              county = "ALLEGHENY",
              survey = "acs5",
              year = 2018)
AlleghenyBlockGroups<-as.data.frame(AlleghenyBlockGroups)

#Tigris boundaries
Allegheny_BG <- block_groups("PA", "Allegheny", year= 2018,)

#setwd("/Users/4victoria98/Downloads/Pittsburgh_Parks")
#parksfile <- st_read("Pittsburgh_Parks.shp")
```

```{r Merge_to_our_maps}
# First Extract Data sets for Black, Population and Median Income

Black <- subset(AlleghenyBlockGroups, variable == "Black") %>% select(GEOID, estimate)
Black <- setNames(Black, c("GEOID","Black"))

Population <- subset(AlleghenyBlockGroups, variable == "Population") %>% select(GEOID, estimate)
Population <- setNames(Population, c("GEOID","Population"))

# now use the SF package to merge these things back to the tract map based on GEOID

Combined <- geo_join (Allegheny_BG, Black, "GEOID", "GEOID" )
Combined <- geo_join (Combined, Population, "GEOID", "GEOID" )

# generate Percent black
Combined$Pct_Black <- Combined$Black/Combined$Population

# get rid of NA
Combined[is.na(Combined)] <- 0

```

```{r Map_tracts}
Combined$INTPTLAT<-as.numeric(Combined$INTPTLAT)
Combined$INTPTLON<-as.numeric(Combined$INTPTLON)
New_combined<-Combined%>%filter(INTPTLAT>=40.37&INTPTLAT<=40.5&INTPTLON>=-80.1&INTPTLON<=-79.87)

# Percent Black

ggplot(New_combined, aes(fill = Pct_Black))+
  geom_sf(, colour = NA) +
  ggtitle("Percent Black in Block Group")+
  geom_sf(data = parksfile, fill= "green") +theme_bw()


```




```{r}
ggplot(Allegheny_BG)+
  geom_sf(data= Allegheny_BG$geometry, fill=NA)+
  geom_sf(data = parksfile, fill= "green") + theme_bw()
```

```{r}
municipalities<-st_read("/Users/4victoria98/Downloads/Capstone/Re_ Pittsburgh Park Conservancy Meeting/LandRecords_LANDRECORDS_OWNER_Municipalities.shp")
```
```{r}
#View(municipalities)
pitt_municipality_shape<-municipalities%>%filter(NAME=="PITTSBURGH")
View(pitt_municipality_shape)
```


#CHANGE THE CRS SO THAT WE CAN FILTER DOWN TO BLOCK GROUPS THAT ARE IN THE PITTSBURGH MUNICIPALITY
```{r}
Pittsburgh_crs <- Pittsburgh1
pitt_municipality_shape_crs <- st_transform(pitt_municipality_shape, "NAD83")
filtered<- Pittsburgh_crs%>%sf::st_filter(pitt_municipality_shape_crs)
st_geometry(Pittsburgh1)
#st_geometry(pitt_municipality_shape)
#newData <- spTransform(Pittsburgh1,CRS(pitt_municipality_shape))
```

```{r}
ggplot(filtered)+
  geom_sf(data= filtered$geometry, fill=NA)+
  geom_sf(data = parksfile, fill= "green") + geom_sf(data=pitt_municipality_shape_crs, fill="blue", alpha=.1, color=NA)
```


```{r}
Allegheny_BG$INTPTLAT<-as.numeric(Allegheny_BG$INTPTLAT)
Allegheny_BG$INTPTLON<-as.numeric(Allegheny_BG$INTPTLON)
Pittsburgh1<-Allegheny_BG%>%filter(INTPTLAT>=40.37&INTPTLAT<=40.5&INTPTLON>=-80.1&INTPTLON<=-79.87)
ggplot(Pittsburgh1)+
  geom_sf(data= Pittsburgh1$geometry, fill=NA)+
  geom_sf(data = parksfile, fill= "green")
```
```{r}
View(parksfile)
```

```{r}
entrance_mellon<-data.frame(x=-79.9191390, y = 40.4518664)
```
```{r}
mellon_park<-Allegheny_BG%>%filter(INTPTLAT>=40.4373664 & INTPTLAT<=(40.4663664)&INTPTLON>=-79.933639&INTPTLON<=-79.904639)
```

```{r}
mellon_park
```

```{r}
View(mellon_park)
```

```{r}
mellon_shape<-parksfile%>%filter(updatepknm=="Mellon Park")
```


```{r}
mellon_park$walk_mins<-0
mellon_park$centroid<-0
mellon_park$centroid<-paste(mellon_park$INTPTLAT, mellon_park$INTPTLON, sep = ", ")

for(i in 1:31){
  mellon_park$walk_mins[i]<-gmapsdistance(origin=mellon_park$centroid[i], destination = "40.4518664, -79.9191390", mode = "walking")$Time / 60
}

```



```{r}
ggplot(mellon_park)+
  geom_sf(data= mellon_park, aes(fill=walk_mins)) +   geom_sf(data = mellon_shape, fill= "green")+ geom_point(aes(x=-79.9191390, y = 40.4518664), color="yellow", size=3) + xlab("Longitude") + ylab("Latitude") + ggtitle("Walking Distance From Mellon Park")+ theme_bw() + labs(fill = "Minutes of Walking")  
```

```{r}
Pittsburgh<-Allegheny_BG%>%filter(INTPTLAT>=40.46462&INTPTLAT<=40.49362&INTPTLON>=-79.9301969&INTPTLON<=-79.9011969)
```



```{r}
Pittsburgh$walk_mins<-0
Pittsburgh$centroid<-0
Pittsburgh$centroid<-paste(Pittsburgh$INTPTLAT, Pittsburgh$INTPTLON, sep = ", ")

for(i in 1:21){
  Pittsburgh$walk_mins[i]<-gmapsdistance(origin=Pittsburgh$centroid[i], destination = "40.4791211, -79.9156969", mode = "walking")$Time / 60
}

```




```{r}

ggplot(Pittsburgh)+
  geom_sf(data= Pittsburgh, aes(fill=walk_mins)) +    geom_sf(data = parks, fill= "green")+ geom_point(aes(x=-79.9156969, y = 40.4791211), color="yellow", size=5) + xlab("Longitude") + ylab("Latitude") + ggtitle("Walking Distance From Highland Park")+ theme_bw() + labs(fill = "Minutes of Walking") #+ scale_fill_viridis_c(option = "magma",begin = 0, end = .99) + 
```


```{r}
Pittsburgh1<-Allegheny_BG%>%filter(INTPTLAT>=40.37&INTPTLAT<=40.5&INTPTLON>=-80.1&INTPTLON<=-79.87)
ggplot(Pittsburgh1)+
  geom_sf(data= Pittsburgh1$geometry, fill=NA)+
  geom_sf(data = parksfile, fill= "green")+
  geom_sf(data= Pittsburgh, aes(fill=walk_mins)) +    geom_sf(data = parks, fill= "green") + geom_point(aes(x=-79.9156969, y = 40.4791211), color="yellow", size=2) + xlab("Longitude") + ylab("Latitude") + ggtitle("Municpality of Pittsburgh")+ theme_bw() + labs(fill = "Minutes of Walking") +
  geom_sf(data= mellon_park, aes(fill=walk_mins)) +   geom_sf(data = mellon_shape, fill= "green")+ geom_point(aes(x=-79.9191390, y = 40.4518664), color="yellow", size=1) 
```

#CREATE SMALL PARKS FILE AND TRY TO GET NEAREST DISTANCES FOR SMALL PARKS
```{r}
small_parks<-parksfile %>% filter(acreage<=1)
```

```{r}
#install.packages("geosphere")
```
```{r}
library(geosphere)
```

#TRY TO GET LATITUDE AND LONGITUDE THEN GET CENTROID
```{r}
small_parks$centroid<-st_centroid(small_parks$geometry)
for(i in 1:73){
  temp<-unlist(small_parks$centroid[i])
  small_parks$center_long[i]<-temp[1]
  small_parks$center_lat[i]<-temp[2]
}
```




#GRAPH TO CHECK
```{r}
practice<-small_parks[5,]
ggplot(practice) + xlab("Longitude") + ylab("Latitude") + ggtitle("Municpality of Pittsburgh")+ theme_bw() + labs(fill = "Minutes of Walking") +    geom_sf(data = practice, fill= "green") + geom_point(aes(x=practice$center_long, y = practice$center_lat), color="yellow", size=8)
```

#COME UP WITH DISTANCE TO NEAREST PARK
```{r}
#WHAT DO I WANT TO DO:
#FOR EACH BG
  # 1.) FIND NEAREST SMALL PARK
  # 2.) CALCULATE WALKING DISTANCE FROM PARK

Pittsburgh1$walk_nearest_park<-999
Pittsburgh1$centroid_as.string<-paste(as.character(Pittsburgh1$INTPTLAT), as.character(Pittsburgh1$INTPTLON), sep = ", ")
small_parks$centroid_as.string<-paste(as.character(small_parks$center_lat), as.character(small_parks$center_long), sep = ", ")


for(i in 1:538){
  dif_lat<-(Pittsburgh1$INTPTLAT[i]-small_parks$center_lat)^2
  dif_lon<-(Pittsburgh1$INTPTLON[i]-small_parks$center_long)^2
  dist<-sqrt(dif_lat+dif_lon)
  min_place<-which.min(dist)

  Pittsburgh1$walk_nearest_park[i]<-gmapsdistance(origin=Pittsburgh1$centroid_as.string[i], destination = small_parks$centroid_as.string[min_place], mode = "walking")$Time / 60
}

```

#COME UP WITH DRIVING DISTANCE TO HIGHLAND PARK
```{r}

parksfile$centroid<-st_centroid(parksfile$geometry)

for(i in 1:213){
  temp<-unlist(parksfile$centroid[i])
  parksfile$center_long[i]<-temp[1]
  parksfile$center_lat[i]<-temp[2]
}

filtered$drive_highland<-999
filtered$centroid_as.string<-paste(as.character(filtered$INTPTLAT), as.character(filtered$INTPTLON), sep = ", ")
parksfile$centroid_as.string<-paste(as.character(parksfile$center_lat), as.character(parksfile$center_long), sep = ", ")
highland<-parksfile%>%filter(origpkname=="Highland Park")
parking_coords=c("40.4748031, -79.9088601", "40.4792359, -79.9133036", "40.4828638, -79.9118076", "40.4858601, -79.9208788")

#parking_longs<-c("-79.9088601", "-79.9133036", "-79.9118076", "-79.9208788")


for(block_group in 1:429){
  dist<-rep(0,4)
  for(coord in 1:4){
    dist[coord]<-gmapsdistance(origin=filtered$centroid_as.string[block_group], destination = parking_coords[coord], mode = "driving")$Time / 60

  }
  filtered$drive_highland[block_group]<-min(dist)
}

```

```{r}
ggplot(filtered)+
  geom_sf(data= filtered, aes(fill=drive_highland)) +   geom_sf(data = highland, fill= "green") + xlab("Longitude") + ylab("Latitude") + ggtitle("Municipality of Pittsburgh")+ theme_bw() + labs(fill = "Driving Time to Highland") 
```

#COME UP WITH DRIVING DISTANCE TO FRICK PARK 
```{r}


filtered$drive_frick<-999
frick<-parksfile%>%filter(origpkname=="Frick Park")
parking_coords=c("40.4465733, -79.9018713", "40.4369412, -79.8967923", "40.4287079, -79.8923032", "40.4263165, -79.9061038", "40.4143663, -79.9166029",  "40.4293789, -79.9135604",  "40.4368397, -79.9084347")

for(block_group in 1:429){
  dist<-rep(0,7)
  for(coord in 1:7){
    dist[coord]<-gmapsdistance(origin=filtered$centroid_as.string[block_group], destination = parking_coords[coord], mode = "driving")$Time / 60

  }
  filtered$drive_frick[block_group]<-min(dist)
}


```

```{r}
ggplot(filtered)+
  geom_sf(data= filtered, aes(fill=drive_frick)) +   geom_sf(data = frick, fill= "green") + xlab("Longitude") + ylab("Latitude") + ggtitle("Municipality of Pittsburgh")+ theme_bw() + labs(fill = "Driving Time to Frick") 
```


#COME UP WITH DRIVING DISTANCE TO RIVERVIEW PARK
```{r}
filtered$drive_riverview<-999
riverview<-parksfile%>%filter(origpkname=="Riverview Park")

parking_coords=c("40.4882787, -80.0219464", "40.4822617, -80.0211579", "40.4819460, -80.0185125", "40.4787574, -80.0199167")

for(block_group in 1:429){
  dist<-rep(0,4)
  for(coord in 1:4){
    dist[coord]<-gmapsdistance(origin=filtered$centroid_as.string[block_group], destination = parking_coords[coord], mode = "driving")$Time / 60

  }
  filtered$drive_riverview[block_group]<-min(dist)
}

```

```{r}
ggplot(filtered)+
  geom_sf(data= filtered, aes(fill=drive_riverview)) +   geom_sf(data = riverview, fill= "green") + xlab("Longitude") + ylab("Latitude") + ggtitle("Municipality of Pittsburgh")+ theme_bw() + labs(fill = "Driving Time to Riverview") 
```


#COME UP WITH DRIVING DISTANCE TO EMERALD VIEW PARK
```{r}

filtered$drive_emerald_view<-999
emerald_view<-parksfile%>%filter(alterntnam=="Emerald View Regional Park")
parking_coords=c("40.4382725, -80.0305674", "40.4330890, -80.0247400", "40.4304558, -80.0192102", "40.4299638, -80.0036075")


for(block_group in 1:429){
  dist<-rep(0,4)
  for(coord in 1:4){
    dist[coord]<-gmapsdistance(origin=filtered$centroid_as.string[block_group], destination = parking_coords[coord], mode = "driving")$Time / 60

  }
  
  filtered$drive_emerald_view[block_group]<-min(dist)
}

```

#COME UP WITH DRIVING DISTANCE TO SCHENLEY VIEW PARK
```{r}

filtered$drive_schenley<-999
schenley<-parksfile%>%filter(alterntnam=="Schenley Park")
parking_coords=c("40.4433531, -79.9528608", "40.4394195, -79.9438876", "40.4359880, -79.9471918", "40.4300965, -79.9503380", "40.4319287, -79.9426842", "40.4306343, -79.9378139", "40.4334242, -79.9343508")


for(block_group in 1:429){
  dist<-rep(0,7)
  for(coord in 1:7){
    dist[coord]<-gmapsdistance(origin=filtered$centroid_as.string[block_group], destination = parking_coords[coord], mode = "driving")$Time / 60

  }
  
  filtered$drive_schenley[block_group]<-min(dist)
}

```


```{r}
ggplot(filtered)+
  geom_sf(data= filtered, aes(fill=drive_emerald_view)) +   geom_sf(data = emerald_view, fill= "green") + xlab("Longitude") + ylab("Latitude") + ggtitle("Municipality of Pittsburgh")+ theme_bw() + labs(fill = "Driving Time to Riverview") 
```




#COME UP WITH WALKING AND TRANSIT DISTANCE TO HIGHLAND PARK
```{r}
filtered$walk_highland<-999

filtered$bus_highland<-999

entrance_coords=c("40.4754078, -79.9106177", "40.4775790, -79.9137116", "40.4786420, -79.9160834", "40.4795241, -79.9186665", "40.4799714, -79.9197147", "40.4874482, -79.9182595", "40.4832795, -79.9084971")


for(block_group in 1:429){
  dist_walk<-rep(0,7)
  dist_bus<-rep(0,7)
  for(coord in 1:7){
    dist_walk[coord]<-gmapsdistance(origin=filtered$centroid_as.string[block_group], destination = entrance_coords[coord], mode = "walking")$Time / 60
    dist_bus[coord]<-gmapsdistance(origin=filtered$centroid_as.string[block_group], destination = entrance_coords[coord], mode = "transit")$Time / 60
  }
  
  filtered$walk_highland[block_group]<-min(dist_walk)
  filtered$bus_highland[block_group]<-min(dist_bus)

}

```

#COME UP WITH WALKING AND TRANSIT DISTANCE TO RIVERVIEW PARK
```{r}
filtered$walk_riverview<-999

filtered$bus_riverview<-999

entrance_coords=c("40.4787562, -80.0120263", "40.4775496, -80.0184257", "40.4795906, -80.0118493", "40.4838777, -80.0132366", "40.4827671, -80.0181776", "40.4860102, -80.0226679", "40.4855066, -80.0234807")


for(block_group in 1:429){
  dist_walk<-rep(0,7)
  dist_bus<-rep(0,7)
  for(coord in 1:7){
    dist_walk[coord]<-gmapsdistance(origin=filtered$centroid_as.string[block_group], destination = entrance_coords[coord], mode = "walking")$Time / 60
    dist_bus[coord]<-gmapsdistance(origin=filtered$centroid_as.string[block_group], destination = entrance_coords[coord], mode = "transit")$Time / 60
  }
  
  filtered$walk_riverview[block_group]<-min(dist_walk)
  filtered$bus_riverview[block_group]<-min(dist_bus)

}

```

#COME UP WITH WALKING AND TRANSIT DISTANCE TO EMERALD VIEW PARK
```{r}
filtered$walk_emerald_view<-999

filtered$bus_emerald_view<-999

entrance_coords=c("40.4390972, -80.0303293", "40.4364092, -80.0274571", "40.4394063, -80.0214194", "40.4356076, -80.0122784", "40.4258173, -79.9924056", "40.4297817, -80.0195278", "40.4323209, -80.0176553", "40.4260500, -80.0162518", "40.4246606, -80.0134702", "40.4301167, -80.0035448", "40.4261947, -79.9976856")


for(block_group in 1:429){
  dist_walk<-rep(0,11)
  dist_bus<-rep(0,11)
  for(coord in 1:11){
    dist_walk[coord]<-gmapsdistance(origin=filtered$centroid_as.string[block_group], destination = entrance_coords[coord], mode = "walking")$Time / 60
    dist_bus[coord]<-gmapsdistance(origin=filtered$centroid_as.string[block_group], destination = entrance_coords[coord], mode = "transit")$Time / 60
  }
  
  filtered$walk_emerald_view[block_group]<-min(dist_walk)
  filtered$bus_emerald_view[block_group]<-min(dist_bus)

}

```

#COME UP WITH WALKING AND TRANSIT DISTANCE TO FRICK PARK
```{r}
filtered$walk_frick<-999

filtered$bus_frick<-999

entrance_coords=c("40.4154867, -79.9171743", "40.4172801, -79.9177389", "40.4250141, -79.9096098", "40.4242909, -79.9048567", "40.4273813, -79.9057078", "40.4318531, -79.8993822", "40.4282536, -79.8923957", "40.4371898, -79.8969786", "40.4395601, -79.8977122", "40.4395575, -79.8993634", "40.4417061, -79.8994466","40.4423607, -79.8993771", "40.4447002, -79.8998902", "40.4458244, -79.9013503", "40.4463066, -79.9032040", "40.4453329, -79.9042321", "40.4392837, -79.9012169", "40.4358128, -79.9092833", "40.4303570, -79.9151294")


for(block_group in 1:429){
  dist_walk<-rep(0,19)
  dist_bus<-rep(0,19)
  for(coord in 1:19){
    dist_walk[coord]<-gmapsdistance(origin=filtered$centroid_as.string[block_group], destination = entrance_coords[coord], mode = "walking")$Time / 60
    dist_bus[coord]<-gmapsdistance(origin=filtered$centroid_as.string[block_group], destination = entrance_coords[coord], mode = "transit")$Time / 60
  }
  
  filtered$walk_frick[block_group]<-min(dist_walk)
  filtered$bus_frick[block_group]<-min(dist_bus)

}

```

#COME UP WITH WALKING AND TRANSIT DISTANCE TO SCHENLEY PARK
```{r}
filtered$walk_schenley<-999

filtered$bus_schenley<-999

entrance_coords=c("40.4433531, -79.9528608", "40.4419450, -79.9526951", "40.4411728, -79.9476851", "40.4404088, -79.9422077", "40.4379740, -79.9333580", "40.4351975, -79.9341185", "40.4345119, -79.9331740", "40.4319537, -79.9331264", "40.4303375, -79.9328958", "40.4365276, -79.9500408", "40.4346630, -79.9484150", "40.4290654, -79.9495110")


for(block_group in 1:429){
  dist_walk<-rep(0,12)
  dist_bus<-rep(0,12)
  for(coord in 1:12){
    dist_walk[coord]<-gmapsdistance(origin=filtered$centroid_as.string[block_group], destination = entrance_coords[coord], mode = "walking")$Time / 60
    dist_bus[coord]<-gmapsdistance(origin=filtered$centroid_as.string[block_group], destination = entrance_coords[coord], mode = "transit")$Time / 60
  }
  
  filtered$walk_schenley[block_group]<-min(dist_walk)
  filtered$bus_schenley[block_group]<-min(dist_bus)
}

```

#Map transit times to Emerald View Park
```{r}
ggplot(filtered)+
  geom_sf(data= filtered, aes(fill=drive_emerald_view)) +   geom_sf(data = emerald_view, fill= "green") + xlab("Longitude") + ylab("Latitude") + ggtitle("Municipality of Pittsburgh")+ theme_bw() + labs(fill = "Driving Time to Emerald View") 
ggplot(filtered)+
  geom_sf(data= filtered, aes(fill=walk_emerald_view)) +   geom_sf(data = emerald_view, fill= "green") + xlab("Longitude") + ylab("Latitude") + ggtitle("Municipality of Pittsburgh")+ theme_bw() + labs(fill = "Walk Time to Emerald View") 
ggplot(filtered)+
  geom_sf(data= filtered, aes(fill=bus_emerald_view)) +   geom_sf(data = emerald_view, fill= "green") + xlab("Longitude") + ylab("Latitude") + ggtitle("Municipality of Pittsburgh")+ theme_bw() + labs(fill = "Busing Time to Emerald View") 
```
#Map transit times to Schenley Park
```{r}
ggplot(filtered)+
  geom_sf(data= filtered, aes(fill=drive_schenley)) +   geom_sf(data = schenley, fill= "green") + xlab("Longitude") + ylab("Latitude") + ggtitle("Municipality of Pittsburgh")+ theme_bw() + labs(fill = "Driving Time to Schenley") 
ggplot(filtered)+
  geom_sf(data= filtered, aes(fill=walk_schenley)) +   geom_sf(data = schenley, fill= "green") + xlab("Longitude") + ylab("Latitude") + ggtitle("Municipality of Pittsburgh")+ theme_bw() + labs(fill = "Walk Time to Schenley") 
ggplot(filtered)+
  geom_sf(data= filtered, aes(fill=bus_schenley)) +   geom_sf(data = schenley, fill= "green") + xlab("Longitude") + ylab("Latitude") + ggtitle("Municipality of Pittsburgh")+ theme_bw() + labs(fill = "Busing Time to Schenley") 
```
#Map transit times to Highland Park
```{r}
ggplot(filtered)+
  geom_sf(data= filtered, aes(fill=drive_highland)) +   geom_sf(data = highland, fill= "green") + xlab("Longitude") + ylab("Latitude") + ggtitle("Municipality of Pittsburgh")+ theme_bw() + labs(fill = "Driving Time to Highland") 
ggplot(filtered)+
  geom_sf(data= filtered, aes(fill=walk_highland)) +   geom_sf(data = highland, fill= "green") + xlab("Longitude") + ylab("Latitude") + ggtitle("Municipality of Pittsburgh")+ theme_bw() + labs(fill = "Walk Time to Highland") 
ggplot(filtered)+
  geom_sf(data= filtered, aes(fill=bus_highland)) +   geom_sf(data = highland, fill= "green") + xlab("Longitude") + ylab("Latitude") + ggtitle("Municipality of Pittsburgh")+ theme_bw() + labs(fill = "Busing Time to Highland") 
```
#Map Transit times to Frick Park
```{r}
ggplot(filtered)+
  geom_sf(data= filtered, aes(fill=drive_frick)) +   geom_sf(data = frick, fill= "green") + xlab("Longitude") + ylab("Latitude") + ggtitle("Municipality of Pittsburgh")+ theme_bw() + labs(fill = "Driving Time to Frick") 
ggplot(filtered)+
  geom_sf(data= filtered, aes(fill=walk_frick)) +   geom_sf(data = frick, fill= "green") + xlab("Longitude") + ylab("Latitude") + ggtitle("Municipality of Pittsburgh")+ theme_bw() + labs(fill = "Walk Time to Frick") 
ggplot(filtered)+
  geom_sf(data= filtered, aes(fill=bus_frick)) +   geom_sf(data = frick, fill= "green") + xlab("Longitude") + ylab("Latitude") + ggtitle("Municipality of Pittsburgh")+ theme_bw() + labs(fill = "Busing Time to Frick") 
```

#View transit times to Riverview Park
```{r}
ggplot(filtered)+
  geom_sf(data= filtered, aes(fill=drive_riverview)) +   geom_sf(data = riverview, fill= "green") + xlab("Longitude") + ylab("Latitude") + ggtitle("Municipality of Pittsburgh")+ theme_bw() + labs(fill = "Driving Time to Riverview") 
ggplot(filtered)+
  geom_sf(data= filtered, aes(fill=walk_riverview)) +   geom_sf(data = riverview, fill= "green") + xlab("Longitude") + ylab("Latitude") + ggtitle("Municipality of Pittsburgh")+ theme_bw() + labs(fill = "Walk Time to Riverview") 
plot<-ggplot(filtered)+
  geom_sf(data= filtered, aes(fill=bus_riverview)) +   geom_sf(data = riverview, fill= "green") + xlab("Longitude") + ylab("Latitude") + ggtitle("Municipality of Pittsburgh")+ theme_bw() + labs(fill = "Busing Time to Riverview") 
```   

```{r}
ggplot(Pittsburgh1)+
  geom_sf(data= Pittsburgh1, aes(fill=walk_nearest_park)) +   geom_sf(data = small_parks, fill= "green") + xlab("Longitude") + ylab("Latitude") + ggtitle("Municipality of Pittsburgh")+ theme_bw() + labs(fill = "Minutes of Walking") 
```

```{r}
Pittsburgh1_smaller<-Pittsburgh1%>%filter(walk_nearest_park<30)
ggplot(Pittsburgh1)+
    geom_sf(data = small_parks, fill= "green") + xlab("Longitude") + ylab("Latitude") + ggtitle("Municpality of Pittsburgh")+ theme_bw() + labs(fill = "Minutes of Walking") + geom_sf(data= Pittsburgh1, fill="white") + geom_sf(data= Pittsburgh1_smaller, aes(fill=walk_nearest_park))
```

#Install and load plotly, the interactive maps package
```{r}
install.packages("plotly")
library(plotly)
```

#CHANGE THE CRS SO THAT WE CAN USE PLOTLY
```{r}
pittsburgh_interactive <- st_transform(filtered, "WGS84")
```

```{r}
pittsburgh_interactive$index<-1:429
```

#Make driving, walking, and busing times numeric values and round to nearest whole number
```{r}

pittsburgh_interactive$drive_frick<-round(as.numeric(pittsburgh_interactive$drive_frick), digits=0)
pittsburgh_interactive$walk_frick<-round(as.numeric(pittsburgh_interactive$walk_frick), digits=0)
pittsburgh_interactive$bus_frick<-round(as.numeric(pittsburgh_interactive$bus_frick), digits=0)

pittsburgh_interactive$drive_highland<-round(as.numeric(pittsburgh_interactive$drive_highland), digits=0)
pittsburgh_interactive$walk_highland<-round(as.numeric(pittsburgh_interactive$walk_highland), digits=0)
pittsburgh_interactive$bus_highland<-round(as.numeric(pittsburgh_interactive$bus_highland), digits=0)

pittsburgh_interactive$drive_schenley<-round(as.numeric(pittsburgh_interactive$drive_schenley), digits=0)
pittsburgh_interactive$walk_schenley<-round(as.numeric(pittsburgh_interactive$walk_schenley), digits=0)
pittsburgh_interactive$bus_schenley<-round(as.numeric(pittsburgh_interactive$bus_schenley), digits=0)

pittsburgh_interactive$drive_riverview<-round(as.numeric(pittsburgh_interactive$drive_riverview), digits=0)
pittsburgh_interactive$walk_riverview<-round(as.numeric(pittsburgh_interactive$walk_riverview), digits=0)
pittsburgh_interactive$bus_riverview<-round(as.numeric(pittsburgh_interactive$bus_riverview), digits=0)

pittsburgh_interactive$drive_emerald_view<-round(as.numeric(pittsburgh_interactive$drive_emerald_view), digits=0)
pittsburgh_interactive$walk_emerald_view<-round(as.numeric(pittsburgh_interactive$walk_emerald_view), digits=0)
pittsburgh_interactive$bus_emerald_view<-round(as.numeric(pittsburgh_interactive$bus_emerald_view), digits=0)

```

#Make interactive map with transit time to highland park
```{r}
plot<-plot_ly(
  pittsburgh_interactive, 
  split = ~index, 
  color=~"blue",
  text = ~paste("Highland Park ", "\nwalk:", walk_highland, "minutes", "\ndriving:", drive_highland, "minutes", "\nbusing:", bus_highland, "minutes"),
  hoveron = "fills",
  hoverinfo = "text",
  showlegend = FALSE
)

plot
```


#Try to download map
```{r}
htmlwidgets::saveWidget(as_widget(plot), "/Users/4victoria98/Downloads/interactive_map.html")
```
#Download filtered as a shape file
```{r}
#st_write(filtered, "/Users/4victoria98/Downloads/Pitssburgh_Transit.shp")
```

#Merge filtered with race data
```{r}
transit_and_black<-filtered
transit_and_black$percent_black<-Combined$Pct_Black
#CHECK IF VECTORS ARE THE SAME
```

```{r}
parks2018<-read_csv('/Users/4victoria98/Downloads/PittParks2018_aggregate.csv')
```


```{r, warnings=FALSE}
highland2018<-parks2018%>%filter(location_name=="Highland Park")

for (i in 1:nrow(highland2018)){
  if (i==1){ #first row create new df
    highlandhomecbgs2018<-unlist(strsplit(highland2018$visitor_home_cbgs[i],","))
    highlandhomecbgs2018<-str_replace_all(highlandhomecbgs2018, '[""]', '')
    highlandhomecbgs2018<-str_replace_all(highlandhomecbgs2018, '[{}]', '')
    highlandhomecbgs2018<-as.data.frame(highlandhomecbgs2018)
    colnames(highlandhomecbgs2018)[1]='GEOID'
    highlandhomecbgs2018$Month<-1
  }
  else{ #all other rows rbind data to df
    temp<-unlist(strsplit(highland2018$visitor_home_cbgs[i],","))
    temp<-str_replace_all(temp, '[""]', '')
    temp<-str_replace_all(temp, '[{}]', '')
    temp<-as.data.frame(temp)
    colnames(temp)[1]='GEOID'
    temp$Month<-i
    highlandhomecbgs2018<-rbind(temp,highlandhomecbgs2018)
  }
}

highlandhomecbgs2018<-separate(highlandhomecbgs2018,GEOID,into=c('GEOID','home_cbg_count'),sep = ':')

#Aggregate Visitors
highlandhomecbgs2018$home_cbg_count<-as.numeric(highlandhomecbgs2018$home_cbg_count)

highland2018_total<-highlandhomecbgs2018 %>%group_by(GEOID)%>%summarise(num = n(),total = sum(home_cbg_count))


highland2018_combined<-geo_join(Pittsburgh,highland2018_total,"GEOID","GEOID",how='left')

highland_map<-parksfile%>%filter(origpkname=="Highland Park")
# get rid of NA
#highland2018_combined[is.na(highland2018_combined)] <- 0

# Put on Map
ggplot(highland2018_combined, aes(fill = log(total)))+
  geom_sf(, colour = NA) +
  scale_fill_viridis_c(option="C",begin = 0, end = .99) + 
   geom_sf(data = highland_map, fill= "forest green")+
  ggtitle("Highland Park Vistor HeatMap All Months 2018")
# divide CBGs into pecentiles (decile?)
```

```{r}
transit_black_cellphone<-transit_and_black
transit_black_cellphone$total<-highland2018_combined$total
```

```{r}
model<-lm(total~walk_highland+bus_highland+drive_highland+percent_black, transit_black_cellphone)
summary(model)
```


```{r, warnings=FALSE}
parks2018<-read_csv('/Users/4victoria98/Downloads/PittParks2018_aggregate.csv')

for (i in 1:nrow(parks2018)){
  if (i==1){ #first row create new df
    parkhomecbgs2018<-unlist(strsplit(highland2018$visitor_home_cbgs[i],","))
    parkhomecbgs2018<-str_replace_all(highlandhomecbgs2018, '[""]', '')
    parkhomecbgs2018<-str_replace_all(highlandhomecbgs2018, '[{}]', '')
    parkhomecbgs2018<-as.data.frame(highlandhomecbgs2018)
    colnames(parkhomecbgs2018)[1]='GEOID'
    parkhomecbgs2018$Month<-1
  }
  else{ #all other rows rbind data to df
    temp<-unlist(strsplit(parks2018$visitor_home_cbgs[i],","))
    temp<-str_replace_all(temp, '[""]', '')
    temp<-str_replace_all(temp, '[{}]', '')
    temp<-as.data.frame(temp)
    colnames(temp)[1]='GEOID'
    temp$Month<-i
    parkhomecbgs2018<-rbind(temp,parkhomecbgs2018)
  }
}

highlandhomecbgs2018<-separate(highlandhomecbgs2018,GEOID,into=c('GEOID','home_cbg_count'),sep = ':')

#Aggregate Visitors
highlandhomecbgs2018$home_cbg_count<-as.numeric(highlandhomecbgs2018$home_cbg_count)

highland2018_total<-highlandhomecbgs2018 %>%group_by(GEOID)%>%summarise(num = n(),total = sum(home_cbg_count))


highland2018_combined<-geo_join(Pittsburgh,highland2018_AVG,"GEOID","GEOID",how='left')

# get rid of NA
#highland2018_combined[is.na(highland2018_combined)] <- 0

# Put on Map
ggplot(highland2018_combined, aes(fill = log(total)))+
  geom_sf(, colour = NA) +
  scale_fill_viridis_c(option="C",begin = 0, end = .99) + 
   geom_sf(data = parksfile, fill= "forest green")+
  ggtitle("Highland Park Vistor HeatMap All Months 2018")
# divide CBGs into pecentiles (decile?)
```

```{r}
library(gmapsdistance)
```


